---
title: "Assignment 3 - Fundamentals of Machine Learning"
output: html_document
date: "2022-10-14"
---

```{r}
library(ISLR)
library(forecast)
library(class)
library(psych) 
library(caret)
library(FNN)
library(melt)
library(MASS) 
library(reshape2) 
library(reshape) 
library(e1071)
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
bank = read.csv("~/Desktop/Fundamentals of Machine Learning/Assignment 2/UniversalBank.csv")
bank$Online = as.factor(bank$Online)
bank$Personal.Loan = as.factor(bank$Personal.Loan)
bank$CreditCard = as.factor(bank$CreditCard)
```

```{r}
train.index <- sample(row.names(bank), dim(bank)[1]*0.6)  
test.index <- setdiff(row.names(bank), train.index) 
train.df <- bank[train.index, ]
test.df <- bank[test.index, ]
train <- bank[train.index, ]
test <- bank[train.index,]
```

```{r}
melted.bank = melt(train, id=c("CreditCard","Personal.Loan"), variable= "Online")
recast.bank=dcast(melted.bank, CreditCard+Personal.Loan~Online)
recast.bank[ ,c(1:2,14)]
```
Note: These numbers were all reading different everytime I knit, even without making any additional changes so I went ahead and left it as it was reading the final time I ran the numbers.

78/(1871+216+835+78)= 2.8%

```{r}
melted.bank1 = melt(train, id=c("Personal.Loan"), variable = "Online")
melted.bank2 = melt(train, id=c("CreditCard"), variable = "Online")
recast.bank1 = dcast(melted.bank1, Personal.Loan~Online)
recast.bank2 = dcast(melted.bank2, CreditCard~Online)
PersonalLoanPivot = recast.bank1[, c(1,13)]
CreditCardPivot = recast.bank2[, c(1,14)]

PersonalLoanPivot
CreditCardPivot
```

```{r}
table(train[, c(14,10)])
table(train[, c(13,10)])
table(train[, c(10)])
```
Note: These numbers were all reading different everytime I knit, even without making any additional changes so I went ahead and left it as it was reading the final time I ran the numbers.

i. 83/(83+199) = 29.4% </br>
ii. 167/(167+115) = 59.2% </br>
iii. 282/(282+2718) = 9.4% </br>
iv. 811/(811+1907) = 29.8% </br>
v. 1599/(1599+1119) = 58.8% </br>
vi. 2718/(2718+282) = 90.6% </br>

```{r}
((83/(83+199))*(167/(167+115))*(282/(282+2718)))/(((83/(83+199))*(167/(167+115))*(282/(282+2718)))+((811/(811+1907))*(1599/(1599+1119))*2718/(2718+282)))
```

```{r}
naive.train = train.df[, c(10,13:14)]
naive.test = test.df[, c(10,13:14)]
naivebayes = naiveBayes(Personal.Loan~.,data=naive.train)
naivebayes
```
The naive bayes output is the same as the previous methods. </br> (.294)(.592)(.094)/((.294)(.592)(.094)+(.298)(.588)(.906)) = .09 </br>
In comparison to E, they are about the same.