---
title: "Assignment 4 - Fundamentals of Machine Learning"
output:
  pdf_document: default
  html_document: default
  word_document: default
date: "2022-10-26"
---

```{r}
library(ISLR)
library(forecast)
library(class)
library(psych) 
library(caret)
library(FNN)
library(melt)
library(MASS) 
library(reshape2) 
library(reshape) 
library(e1071)
library(stats)
library (dplyr)
library(ggplot2)
library(ggfortify)
library(factoextra)
library(NbClust)
library(flexclust)
library(dendextend)
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
A. 
```{r}
rm(list = ls())
set.seed(1)
pharmaceutical_data <- read.csv("Pharmaceuticals.csv", header = TRUE)
row.names(pharmaceutical_data) <- pharmaceutical_data[,2]
pharmaceutical_data <- pharmaceutical_data[, -c(1,2,12,13,14)]
pharmaceutical_data.norm <- sapply(pharmaceutical_data, scale)

pharmaceutical_data.norm
pharmaceutical_data <- pharmaceutical_data.norm
```
B.
```{r}
pharmaceutical_data <- scale(pharmaceutical_data)
distance <- get_dist(pharmaceutical_data)
fviz_dist(distance)
```

```{r}
k4 <- kmeans (pharmaceutical_data, centers = 4, nstart = 25)
k4$centers
k4$size
k4$cluster[120]
fviz_cluster(k4, data = pharmaceutical_data)
```

```{r}
set.seed(123)
k4 = kcca(pharmaceutical_data, k=4, kccaFamily("kmedians"))
k4
```

```{r}
clusters_index <- predict(k4)
dist(k4@centers)
image(k4)
points(pharmaceutical_data, col= clusters_index, pch = 19, cex=.3)
```

```{r}
set.seed(123)
pharmaceutical_data <- Auto[,c(1,6)]
pharmaceutical_data <- scale (pharmaceutical_data)
fviz_nbclust(pharmaceutical_data, kmeans, method = "wss")
```

```{r}
fviz_nbclust (pharmaceutical_data, kmeans, method = "silhouette")
```

```{r}
nc <- NbClust(pharmaceutical_data.norm, distance="euclidean", min.nc=2, max.nc=10, method="average")

table(nc$Best.n[1,])

barplot(table(nc$Best.n[1,]), xlab="Clusters (Amount)", ylab="Criteria (Amount)", main="# of Clusters By Using Criteria")
d <- dist(pharmaceutical_data.norm)
```

```{r}
AverageClust <- hclust(d, method="average")

plot(AverageClust, hang = -1, cex=0.8, main="average linkage clustering")

clusters <- cutree(AverageClust, k=6)

aggregate(pharmaceutical_data.norm, by=list(cluster=clusters), median)
rect.hclust(AverageClust, k=6)

clust.means <- function(x, res.clust, groups)
{
  if(!is.matrix(x))
    x <- as.matrix(x)
  means <- tapply(x, list(rep(cutree(res.clust, groups), ncol(x)),
                          col(x)),
                  mean)
  dimnames(means) <- list(NULL, dimnames(x)[[2]])
  return(as.data.frame(means))
}


PharmaCentroids<-clust.means(pharmaceutical_data.norm, AverageClust, 6)

y<-apply(as.matrix(PharmaCentroids), 2, as.double)

plot(c(0), xaxt = 'n', ylab = "", type = "l", ylim = c(min(y), max(y)), xlim = c(0,9))

axis(1, at = c(1:9), labels = names(pharmaceutical_data))

for (i in c(1:6))
  lines(y[i,],  lty = i, lwd = 2,
        col = ifelse(i %in% c(1),"pink",
                     (ifelse(i %in% c(2),"green",
                             (ifelse(i %in% c(3),"blue",
                                     (ifelse(i %in% c(4,5),"black","orange"))))))))

text(x = 0.5, y = PharmaCentroids[, 1], labels = paste("Cluster", c(1:6)))
```

C.
I would not necessarily say there is a pattern in the clusters with repsect to the numerical variables. The median recommendation helps us understand if each cluster is a buy, hold or sell. It helps to read the cluster graphs in double checking if you feel these recommendations are reliable.

D. 
Cluster 1 is our "steady" cluster. It remains mostly in the middle of the graph the entire time.
Cluster 2 is "Stable but low Profit margin" by having high PE Ratio but low profit margin.
Cluster 3 is the "high risk, low reward". It shoots up for Beta but takes a dive afterwards.
Cluster 4 is "high risk, good outcome".
Cluster 5 is similar to 3. The risk is high but profit is average so it would be called "high risk, medium payout".
Cluster 6 starts out with the highest market cap and very low risk. It finishes somewhere in the middle range for profit. I'd call this "the chosen cluster".
